### 2015-05-16 Irregulares/Irregulares.tex
Adicionado Artigos dos irregulares e de Ceres

%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,traditabstract, referee]{aa}
\usepackage[varg]{txfonts}
%\usepackage[english,brazilian]{babel}
\usepackage[T1]{fontenc}
\setcounter{tocdepth}{3}
\usepackage{prettyref}
\usepackage{array}
\usepackage{rotating}
\usepackage{float}
\usepackage{multirow}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{gensymb}
\usepackage{longtable}
%\usepackage{setspace}
%
%\usepackage{etoolbox}
%\AtBeginEnvironment{longtable}{\singlespacing}
%\setlength{\LTcapwidth}{\linewidth}

@@

\title{Astrometric positions for 18 irregular satellites of giant planets from 23 years of observations
\fnmsep\thanks{The complete version of Table 8 is available through CDS and IAU NSDC data base at www.imcce.fr/nsdc.}
\fnmsep\thanks{Partially based on observations made at Laborat\'orio Nacional de Astrof\'{\i}sica (LNA), Itajub\'a-MG, Brazil.}
\fnmsep\thanks{Partially based on observations through the ESO runs 079.A-9202(A), 075.C-0154, 077.C-0283 and 079.C-0345.}
\fnmsep\thanks{\textbf{Partially based on observations made at
Observatoire de Haute Provence (OHP), F-04870 Saint-Michel l'observatoire, France}}
}

\author{ A. R. Gomes-Júnior
          \inst{1},
          M. Assafin 
          \inst{1} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          R. Vieira-Martins
          \inst{1,2,3} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          J.-E. Arlot
          \inst{4},      
          J. I. B. Camargo
          \inst{2,3},     
          F. Braga-Ribas
          \inst{2,5}, 
          D. N. da Silva Neto
          \inst{6},
          A. H. Andrei
          \inst{1,2} \fnmsep\thanks{Affiliated researcher at the Observatoire de Paris/SYRTE, 77 av. Denfert Rochereau, 75014 Paris, France},
          A. Dias-Oliveira
          \inst{2},
          B. E. Morgado
          \inst{1},
          G. Benedetti-Rossi
          \inst{2},
          Y. Duchemin
          \inst{4,7},
          J. Desmars
          \inst{4},
          V. Lainey
          \inst{4},
          W. Thuillot
          \inst{4}
          }

>>>>

%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,traditabstract]{aa}
\usepackage[varg]{txfonts}
%\usepackage[english,brazilian]{babel}
\usepackage[T1]{fontenc}
\setcounter{tocdepth}{3}
\usepackage{prettyref}
\usepackage{array}
\usepackage{rotating}
\usepackage{float}
\usepackage{multirow}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{gensymb}
\usepackage{longtable}
%\usepackage{setspace}
%
%\usepackage{etoolbox}
%\AtBeginEnvironment{longtable}{\singlespacing}
%\setlength{\LTcapwidth}{\linewidth}

@@

\title{Astrometric positions for 18 irregular satellites of giant planets from 23 years of observations
\fnmsep\thanks{Table 8 are only available in electronic form
at the CDS via anonymous ftp to cdsarc.u-strasbg.fr (130.79.128.5)
or via http://cdsweb.u-strasbg.fr/cgi-bin/qcat?J/A+A/ and IAU NSDC data base at www.imcce.fr/nsdc.}
%\fnmsep\thanks{The complete version of Table 8 is available through CDS and IAU NSDC data base at www.imcce.fr/nsdc.}
\fnmsep\thanks{Partially based on observations made at Laborat\'orio Nacional de Astrof\'{\i}sica (LNA), Itajub\'a-MG, Brazil.}
\fnmsep\thanks{Partially based on observations through the ESO runs 079.A-9202(A), 075.C-0154, 077.C-0283 and 079.C-0345.}
\fnmsep\thanks{\textbf{Partially based on observations made at
Observatoire de Haute Provence (OHP), F-04870 Saint-Michel l'observatoire, France}}
}

\author{ A. R. Gomes-Júnior
          \inst{1},
          M. Assafin 
          \inst{1} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          R. Vieira-Martins
          \inst{1,2,3} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          J.-E. Arlot
          \inst{4},      
          J. I. B. Camargo
          \inst{2,3},     
          F. Braga-Ribas
          \inst{2,5}, 
          D. N. da Silva Neto
          \inst{6},
          A. H. Andrei
          \inst{1,2} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau, 75014 Paris, France},
          A. Dias-Oliveira
          \inst{2},
          B. E. Morgado
          \inst{1},
          G. Benedetti-Rossi
          \inst{2},
          Y. Duchemin
          \inst{4,7},
          J. Desmars
          \inst{4},
          V. Lainey
          \inst{4},
          W. Thuillot
          \inst{4}
          }
